\documentclass[a4paper, 12pt]{report}
\textwidth = 14.5cm \textheight = 21.5cm \topmargin = -.5cm
\leftmargin = 5cm

\setcounter{secnumdepth}{2} \setcounter{tocdepth}{3}

%\oddsidemargin = 1cm
%\leftmargin = -3cm
%\evensidemargin = 5cm


%\includeonly{eqrmtech-h-apps}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancybox}
\usepackage{natbib}
\bibliographystyle{grfchicago}
\usepackage{makeidx}
\usepackage{url}
\usepackage{psfrag}
\usepackage{supertabular}
\usepackage{drcaptionstyle}
\usepackage{listings}
%\usepackage{color}
\usepackage[usenames,dvipsnames]{color}
\usepackage{lscape}
\usepackage{multirow}
%\usepackage{bbding}
%\usepackage{epstopdf}

% set up some environments
\definecolor{light-gray}{gray}{0.8}
\lstset{basicstyle=\scriptsize}
%\lstset{frame=shadowbox, rulesepcolor=\color{blue}, fillcolor = \color{blue}} % create a frame and blue boundary for the xml file
\lstset{frame=single, backgroundcolor=\color{light-gray}}


\graphicspath{{diags/}}

\input eqrmtech-macros

\setlength{\parskip}{1em plus 0.1em minus 0.2em}
\setlength{\parindent}{0pt}


\makeindex



\title{EQRM: Geoscience Australia's Earthquake Risk Model\\
}

%\begin{center}
% Version 2.0
%\end{center}

\author{Technical Manual \\[1em]
Version 3.0 \\[3em]
David Robinson, Glenn Fulford and Trevor Dhu\\[1em]
Geoscience Australia}



\begin{document}
\maketitle

\pagenumbering{roman}

this is a blank page \newpage


this is a blank page
\newpage

 {\Huge \textbf{Acknowledgements}  }

The authors wish to thank John Schneider, leader of the Risk
Research Group at Geoscience Australia. John's expertise in the
areas of earthquake hazard and risk analysis have proven
invaluable throughout the project. Without his ongoing support and
advice the EQRM would not be half the product that it is today.

Andres Mendez from Aon Re in Chicago is acknowledged for providing
software that formed the backbone of the earthquake catalogue
generation. This generous contribution, as well as his high level
of collaborative support, was fundamental to the project's
success.

Bradley Horton is appreciated for the programming support that he
provided through a number of contracts with Ceanet. The
professionalism with which Bradley conducted his work extended
beyond the call of duty on many occasions. Bradley's efforts have
lead to great improvements in the useability and robustness of the
EQRM. Duncan Gray, Kurt Pudniks and Ken Dale, all of Geoscience
Australia, are also acknowledged for their coding efforts in
particular modules of the EQRM software.

The authors have sought advice on specific topics from a range of
people involved in the earthquake hazard and risk fields. The
following are acknowledged for their expertise and assistance;
George Walker of Aon Re, Professor John McAneney of Risk
Frontiers, Walt Silva of Pacific Engineering and Analysis, Don
Windeler and his team at Risk Management Solutions (RMS), Mike
Griffith at The University of Adelaide, Gary Gibson of the
Seismology Research Centre and Brian Gaull from Guria Consulting.

A number of people at Geoscience Australia have contributed
 to the development of the EQRM. Members of the Newcastle
and Lake Macquarie project team lead by Trevor Jones are
acknowledged for their assistance in shaping the early design of
the EQRM. Mark Edwards and Ken Dale are thanked for the countless
engineering questions that they have fielded over the four year
project. Matt Hayne, project leader of the Risk Assessment Methods
Project is thanked for creating the productive and supportive
environment that allowed this project to flourish. EQRM users,
Cvetan Sinadinovski, Annette Patchett, Ken Dale and Augusto
Sanabria are thanked for their feedback and for continually
inspiring the incorporation of new functionality. Ole Nielsen and
Duncan Gray are acknowledged for the provision of software
engineering advice and for generally improving the coding
abilities of the authors. Angie Jaensch, Greg Michalowski and
Fiona Watford are acknowledged for drafting some of the figures.
Finally, the authors wish to thank Adrian Hitchman, Ken Dale and
Augusto Sanabria for reviewing the drafts of this report. Their
reviews lead to substantial improvements to this manual.


\tableofcontents

\newpage
\pagenumbering{arabic}
\include{eqrmtech-intro}
\include{eqrmtech-hv-application}
\include{eqrmtech-h-source}
\include{eqrmtech-h-attn}
%\include{eqrmtech-h-regolith}
\include{eqrmtech-v-damage}
\include{eqrmtech-v-losses}
\include{eqrmtech-v-risk}

\appendix
\include{eqrmtech-apps}

\small
\bibliography{drrefs,garefs,EQRM_refs}
%\bibliography{eqrmtech.bbl}
\printindex

\end{document}
